ISSSV1337 Group 5 Report

### 2022-08-03 Report/Group 5 report.Rmd
A space, for safety.

```{r dashboard_images, out.width="50%", fig.cap="The dashboard.", fig.subcap=c("The main page.", "The details tab."), echo=FALSE}
knitr::include_graphics("Images/Dashboard_page_1.png")
knitr::include_graphics("Images/Dashboard_page_2.png")
```
#### Key Performance Indicators

>>>>

```{r dashboard_images, out.width="50%", fig.cap="The dashboard.", fig.subcap=c("The main page.", "The details tab."), echo=FALSE}
knitr::include_graphics("Images/Dashboard_page_1.png")
knitr::include_graphics("Images/Dashboard_page_2.png")
```

#### Key Performance Indicators
